A pandemic-scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-09-29 latex/main.tex
Updates from Overleaf

Of the 21 XAF samples in the Viridian v04 dataset,
only XAF sample passed our QC filters and was added to the ARG:
many have missing Ns in their consensus sequences (> 500) or
require a large number of mutations to incorporate into the ARG
(i.e. have a high HMM cost).
However, we find a small recombinant BA1.1/BA.2 clade of 37 samples,
associated with the BA.2-labeled sample ERR9755541,
within which the single XAF sample is nested.
The inferred parents and breakpoint at 10,447
aligns with that proposed for XAF
(https://github.com/cov-lineages/pango-designation/issues/676).
Inspection of the omitted XAF samples with high HMM cost shows that
they would attach as close sisters to the included XAF sample,
albeit on branches with many new mutations.
Hence we believe the current XAF topology in the ARG is reasonable,
although somewhat tentative, given the number of included samples.

>>>>

Of the 21 XAF samples in the Viridian v04 dataset,
only XAF sample passed our QC filters and was added to the ARG:
many have greater than 500 missing Ns in their consensus sequences or
require a large number of mutations to incorporate into the ARG
(i.e. have a high HMM cost).
However, we find a small recombinant BA1.1/BA.2 clade of 37 samples,
associated with the BA.2-labeled sample ERR9755541,
within which the single XAF sample is nested.
The inferred parents and breakpoint at 10,447
aligns with that proposed for XAF
(https://github.com/cov-lineages/pango-designation/issues/676).
Inspection of the omitted XAF samples with high HMM cost shows that
they would attach as close sisters to the included XAF sample,
albeit on branches with many new mutations.
Hence we believe the current XAF topology in the ARG is reasonable,
although somewhat tentative, given the number of included samples.
